### 2017-02-03 local-capability-machine.tex
A few fixes to awkward example proof (overlooked in previous change)

                  \item Show: $\iota^{\nwl,p}_{\start_\adv,\addrend_\adv} \nsubsim[n] \iota^\pwl_{\start_\adv,\addrend_\adv}$: $\iota^{\nwl,p}_{\start_\adv,\addrend_\adv}
                    \nsubsim[n] \iota^\pwl_{\start_\adv,\addrend_\adv}$: see Lemma~\ref{lem:nwlp-subset-pwl}.

@@

                        SFTS $\iota_{\link} \nsubsim[n'] \iota^\pwl_{\link,\link+1}$\\

@@

                        \item $\npair[n'-1]{c_\malloc} \in \stdvr(W)$: We assume
                          this is indeed the case.\dominique{TODO: prove}
                        \item $\npair[n'-1]{c_\adv} \in \stdvr(W)$: for $n'' <
                          n'-1$ and $W' \futurestr W$ show:
                          \\$\npair[n'']{\updatePcPerm{c_\adv}} \in \stdvr(W')$.
                          Use FTLR.\dominique{no: by induction hypothesis?} \label{f1:adv}

@@

    \iota^{\nwl,p}_{\start_\adv,\addrend_\adv} \nsubsim[n] \iota^\pwl_{\start_\adv,\addrend_\adv}

@@

          \iota^\pwl_{\start_\stk'', \addrend_\stk} \nsubsim[n] \iota^\pwl_{\start_\stk'', \addrend_\stk}
        which is trivially the case.

@@

            \iota^\pwl_{\start_\stk'', \addrend_\stk} \nsubsim[n'] \iota^\pwl_{\start_\stk'', \addrend_\stk}
          which is trivially the case.

@@

          Showing
          \[
            \npair[n]{\ms_\adv} \in H^\sta_{\start_\adv,\addrend_\adv}(1)(\xi^{-1}(W_{\var{mini}}))
          \]
          is a bit more involved. It amounts to 
          \[
            \forall \addr \in \dom(\ms_\adv) \ldotp \npair[n-1]{\ms_\adv(\addr)} \in \stdvr(W_{\var{mini}})
          \]
          which in turn is trivial for everything but
          \[
            \npair[n-1]{c_\link} \in \stdvr(W_{\var{mini}})
          \]
          This amounts to showing
          \[
            \npair[n-1]{(\link,\link)} \in \readCond{}(\glob)(W_{\var{mini}})
          \]
          which amounts to
          \[
            \iota^{\sta,u} (\perma,\ms_\link) \nsubsim[n-1] \iota^\pwl_{\link,\link}
          \]
          which follows from Lemma~\ref{lem:stau-subset-pwl}.
      \end{enumproof}
      Using Lemma~\ref{lem:disj-mem-sat} repeatedly with the above gives the desired memory satisfaction.
    \item $\npair{\reg_0\update{r_\stk}{c_\stk}\update{r_1}{c_{g1}}} \in \stdrr(W)$\\
      This amounts to showing
      \begin{enumproof}
        \item $\npair{\reg_0\update{r_\stk}{c_\stk}\update{r_1}{c_{g1}}(c_\stk)} \in \stdvr(W)$ \\
          The assumptions on $c_\stk$ and $\ms_\stk$ in the lemma entail
          \begin{itemize}
          \item \pointstostack{\reg_0\update{r_\stk}{c_\stk}\update{r_1}{c_{g1}}}{\emptyset}{\ms_\stk}
          \end{itemize}
          and further there is a $\iota^\pwl$ region for $\ms_\stk$ in $W$, so the result follows from Lemma~\ref{stack-cap-vr}.
        \item $\npair{c_{g1}} \in \stdvr(W)$ \\
          Let $n_1 < n$ and $W_1 \futurestr W$ and show
          \[
            \npair[n_1]{\updatePcPerm{c_{g1}}} \in \stder(W_1)
          \]
          To this end assume $n_2 \leq n_1$, $\memSat[n_2]{\ms_1}{W_1}$, and $\npair[n_2]{\reg_1} \in \stdrr(W_1)$ and show
          \[
            \npair[n_2]{(\reg_1\update{\pcreg}{\updatePcPerm{c_{g1}}},\ms_1)} \in \observations(W_1)
          \]
          %TODO elaborate on what happens here using anti reduction lemma and malloc spec.
          Use Lemma~\ref{lem:anti-red-obs}, so let $\ms_f'$ be given, then
          \[
            (\reg_1\update{\pcreg}{\updatePcPerm{c_{g1}}},\ms_1 \uplus \ms_f') \step[i] (\reg_2,\ms_2 \uplus \ms_\malloc' \uplus \ms_\env \uplus \ms_x \uplus \ms_\cls \uplus \ms_f')
          \]
          for some $i$. Where
          \begin{itemize}
          \item $\memSat[n_2-i]{\ms_2 \uplus \ms_\malloc'}{W_1\update{4}{\iota_\malloc}} $
          \item $\iota_\malloc \futurewk \iota_{\malloc,0}$
          \item $\ms_x = [x \mapsto 0]$
          \item $c_x = ((\rwx,\glob),x,x,x)$
          \item $\ms_\env = [\env \mapsto c_x]$
          \item $c_\env = ((\rwx,\glob,\env,\env,\env))$
          \item $c_{f4}$ is $c_{g1}$ updated to point at $f4$.
          \item $\ms_\cls$ contains $c_\env$, the $c_{f4}$, and the activation code.
          \item $c_\cls$ is a global enter capability for $\ms_\cls$ pointing to the activation code.
          \item $\reg_2 = reg_0\update{\pcreg}{\updatePcPerm{\reg_1(r_0)}}\update{r_0}{\reg_1(r_0)}\update{r_1}{c_\cls}$
          \end{itemize}
          For world
          \[
            W_2 = W_1\update{4}{\iota_\malloc}\update{i_1}{\iota^\sta (\perm,\ms^\env \uplus \ms^\cls)}\update{i_2}{\iota_x}
          \]
          where $i_1,i_2\not\in\dom(W_1)$ and $i_1 \neq i_2$ and $\iota_x$ is the region in Definition~\ref{def:iotax-region} which is a region by Lemma~\ref{lem:iotax-is-a-region}.
          Show
          \begin{equation}
            \label{eq:g1-obs-to-show}
            \npair[n_2-i]{(\reg_2,\ms_2 \uplus \ms_\malloc' \uplus \ms_\env \uplus \ms_x \uplus \ms_\cls)} \in \observations(W_2)
          \end{equation}
          If $\reg_1(r_0).\perm \not\in \{\entry, \exec, \rwx, \rwlx\}$, then the execution fails after the jump and \label{eq:g1-obs-to-show} is thus trivially true.

@@

\begin{lemma}
  \label{lem:stau-subset-pwl}
  \begin{align*}
    & \forall n \in \nats\ldotp \forall \start, \addrend \in \Addrs \ldotp \forall v \in \{\perma, \temp\} \ldotp \\
    & \quad \dom(\ms) = [\start,\addrend] \Rightarrow \\
    & \qquad \iota^{\sta,u}_{\start,\addrend}(v,\ms) \nsubsim \iota^\pwl_{\start,\addrend}
  \end{align*}
  \dominique{err.. shouldn't you require that $\npair{\ms(a)}\in\stdvr(W)$ for
    all $W$.  Hm: this probably doesn't hold like that?}
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:stau-subset-pwl}]
  Essentially the same as the proof of Lemma~\ref{lem:nwl-subset-pwl} and Lemma~\ref{lem:hwnl-nsubset-hpwl}.
\end{proof}

@@

\begin{lemma}
  \label{lem:revoketemp-readcond}
  If
  \[
    \npair{(\start,\addrend)} \in \readCond{}(\gl)(\revokeTemp{W})
  \]
  then
  \[
    \npair{(\start,\addrend)} \in \readCond{}(\gl)(W)
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:revoketemp-readcond}]
  \[
    \npair{(\start,\addrend)} \in \readCond{}(\gl)(\revokeTemp{W})
  \]
  Gives $r \in \localityReg(\gl,\revokeTemp{W})$ such that
  \[
    \forall [\start',\addrend'] \subseteq [\start,\addrend] \ldotp \revokeTemp{W}(r) \nsubsim[n] \iota^\pwl_{[\start',\addrend']}
  \]
  Notice $\revokeTemp{W}(r)$ is a $\perma$ region, so $\revokeTemp{W}(r) = W(r)$. Using $r$ as witness, the result is immediate.
\end{proof}

@@

 \begin{lemma}[pwl writecond implies nwl]
   \label{lem:pwl-writecond-implies-nwl}
   If $\npair{(\start,\addrend)} \in \writeCond{}(\iota^\pwl,\gl)(W)$ then
   $\npair{(\start,\addrend)} \in \writeCond{}(\iota^\nwl,\gl)(W) \}$.
 \end{lemma}
 \begin{proof}
   \begin{enumproof}
   \item $\exists r \in \var{localityReg}(g,W) \ldotp$ $\exists
     [\start',\addrend'] \supseteq [\start,\addrend] \ldotp$ $W(r)\nsupsim[n-1]
     \iota^\pwl_{\start',\addrend'}$: by definition of $\writeCond{}$.
   \item Suffices: $W(r)\nsupsim[n-1] \iota^\nwl_{\start',\addrend'}$. By
     definition of $\writeCond{}$
   \item $W(r)\nsupsim[n-1] \iota^\pwl_{\start',\addrend'} \nsupsim[n-1]
     \iota^\nwl_{\start',\addrend'}$: follows by Lemma~\ref{lem:nwl-subset-pwl}.
   \end{enumproof}
 \end{proof}

@@

   then  $\npair{((\perm',\gl'),\start,\addrend,\addr)}\in \stdvr(W)$
 \end{lemma}
 \begin{proof}
   By inspection of the definition of $\stdvr(W)$, everything follows trivially
   except the result from lemma~\ref{lem:pwl-writecond-implies-nwl}.

    If $\npair{(\start,\addrend)} \in \writeCond{}(\iota^\pwl,\gl)(W)$ then $\npair{(\start,\addrend)} \in \writeCond{}(\iota^\nwl,\gl)(W) \}$

  \end{enumproof}
 \end{proof}

>>>>

                  \item Show: $\iota^{\nwl,p}_{\start_\adv,\addrend_\adv} \nsubsim[n-1] \iota^\pwl_{\start_\adv,\addrend_\adv}$. %Lemma

@@

                        SFTS $\iota_{\link} \nsubsim[n'-1] \iota^\pwl_{\link,\link+1}$\\

@@

                        \item $\npair[n'-2]{c_\malloc} \in \stdvr(W)$: We assume this is indeed the case.
                        \item $\npair[n'-2]{c_\adv} \in \stdvr(W)$: for $n'' < n'-2$ and $W' \futurestr W$ show: \\$\npair[n'']{\updatePcPerm{c_\adv}} \in \stdvr(W')$. Use FTLR. \label{f1:adv}

@@

    \iota^{\nwl,p}_{\start_\adv,\addrend_\adv} \nsubsim[n-1] \iota^\pwl_{\start_\adv,\addrend_\adv}

@@

          \iota^\pwl_{\start_\stk'', \addrend_\stk} \nsubsim[n-1] \iota^\pwl_{\start_\stk'', \addrend_\stk}

@@

            \iota^\pwl_{\start_\stk'', \addrend_\stk} \nsubsim[n'-1] \iota^\pwl_{\start_\stk'', \addrend_\stk}

@@

          Showing
          \[
            \npair[n]{\ms_\adv} \in H^\sta_{\start_\adv,\addrend_\adv}(1)(\xi^{-1}(W_{\var{mini}}))
          \]
          is a bit more involved. It amounts to 
          \[
            \forall \addr \in \dom(\ms_\adv) \ldotp \npair[n-1]{\ms_\adv(\addr)} \in \stdvr(W_{\var{mini}})
          \]
          which in turn is trivial for everything but
          \[
            \npair[n-1]{c_\link} \in \stdvr(W_{\var{mini}})
          \]
          This amounts to showing
          \[
            \npair[n-1]{(\link,\link)} \in \readCond{}(\glob)(W_{\var{mini}})
          \]
          which amounts to
          \[
            \iota^{\sta,u} (\perma,\ms_\link) \nsubsim[n-2] \iota^\pwl_{\link,\link}
          \]
          which follows from Lemma~\ref{lem:stau-subset-pwl}.
      \end{enumproof}
      Using Lemma~\ref{lem:disj-mem-sat} repeatedly with the above gives the desired memory satisfaction.
    \item $\npair{\reg_0\update{r_\stk}{c_\stk}\update{r_1}{c_{g1}}} \in \stdrr(W)$\\
      This amounts to showing
      \begin{enumproof}
        \item $\npair{\reg_0\update{r_\stk}{c_\stk}\update{r_1}{c_{g1}}(c_\stk)} \in \stdvr(W)$ \\
          The assumptions on $c_\stk$ and $\ms_\stk$ in the lemma entail
          \begin{itemize}
          \item \pointstostack{\reg_0\update{r_\stk}{c_\stk}\update{r_1}{c_{g1}}}{\emptyset}{\ms_\stk}
          \end{itemize}
          and further there is a $\iota^\pwl$ region for $\ms_\stk$ in $W$, so the result follows from Lemma~\ref{stack-cap-vr}.
        \item $\npair{c_{g1}} \in \stdvr(W)$ \\
          Let $n_1 < n$ and $W_1 \futurestr W$ and show
          \[
            \npair[n_1]{\updatePcPerm{c_{g1}}} \in \stder(W_1)
          \]
          To this end assume $n_2 \leq n_1$, $\memSat[n_2]{\ms_1}{W_1}$, and $\npair[n_2]{\reg_1} \in \stdrr(W_1)$ and show
          \[
            \npair[n_2]{(\reg_1\update{\pcreg}{\updatePcPerm{c_{g1}}},\ms_1)} \in \observations(W_1)
          \]
          % TODO elaborate on what happens here using anti reduction lemma and malloc spec.
          Use Lemma~\ref{lem:anti-red-obs}, so let $\ms_f'$ be given, then
          \[
            (\reg_1\update{\pcreg}{\updatePcPerm{c_{g1}}},\ms_1 \uplus \ms_f') \step[i] (\reg_2,\ms_2 \uplus \ms_\malloc' \uplus \ms_\env \uplus \ms_x \uplus \ms_\cls \uplus \ms_f')
          \]
          for some $i$. Where
          \begin{itemize}
          \item $\memSat[n_2-i]{\ms_2 \uplus \ms_\malloc'}{W_1\update{0}{\iota_\malloc}} $
          \item $\iota_\malloc \futurewk \iota_{\malloc,0}$
          \item $\ms_x = [x \mapsto 0]$
          \item $c_x = ((\rwx,\glob),x,x,x)$
          \item $\ms_\env = [\env \mapsto c_x]$
          \item $c_\env = ((\rwx,\glob,\env,\env,\env))$
          \item $c_{f4}$ is $c_{g1}$ updated to point at $f4$.
          \item $\ms_\cls$ contains $c_\env$, the $c_{f4}$, and the activation code.
          \item $c_\cls$ is a global enter capability for $\ms_\cls$ pointing to the activation code.
          \item $\reg_2 = reg_0\update{\pcreg}{\updatePcPerm{\reg_1(r_0)}}\update{r_0}{\reg_1(r_0)}\update{r_1}{c_\cls}$
          \end{itemize}
          For world
          \[
            W_2 = W_1\update{0}{\iota_\malloc}\update{i_1}{\iota^\sta (\perm,\ms^\env \uplus \ms^\cls)}\update{i_2}{\iota_x}
          \]
          where $i_1,i_2\not\in\dom(W_1)$ and $i_1 \neq i_2$ and $\iota_x$ is the region in Definition~\ref{def:iotax-region} which is a region by Lemma~\ref{lem:iotax-is-a-region}.
          Show
          \begin{equation}
            \label{eq:g1-obs-to-show}
            \npair[n_2-i]{(\reg_2,\ms_2 \uplus \ms_\malloc' \uplus \ms_\env \uplus \ms_x \uplus \ms_\cls)} \in \observations(W_2)
          \end{equation}
          If $\reg_1(r_0).\perm \not\in \{\entry, \exec, \rwx, \rwlx\}$, then the execution fails after the jump and \label{eq:g1-obs-to-show} is thus trivially true.

@@

\begin{lemma}
  \label{lem:stau-subset-pwl}
  \begin{align*}
    & \forall n \in \nats\ldotp \forall \start, \addrend \in \Addrs \ldotp \forall v \in \{\perma, \temp\} \ldotp \\
    & \quad \dom(\ms) = [\start,\addrend] \Rightarrow \\
    & \qquad \iota^{\sta,u}_{\start,\addrend}(v,\ms) \nsubsim \iota^\pwl_{\start,\addrend}
  \end{align*}
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:stau-subset-pwl}]
  Essentially the same as the proof of Lemma~\ref{lem:nwl-subset-pwl} and Lemma~\ref{lem:hwnl-nsubset-hpwl}.
\end{proof}

@@

\begin{lemma}
  \label{lem:revoketemp-readcond}
  If
  \[
    \npair{(\start,\addrend)} \in \readCond{}(\gl)(\revokeTemp{W})
  \]
  then
  \[
    \npair{(\start,\addrend)} \in \readCond{}(\gl)(W)
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:revoketemp-readcond}]
  \[
    \npair{(\start,\addrend)} \in \readCond{}(\gl)(\revokeTemp{W})
  \]
  Gives $r \in \localityReg(\gl,\revokeTemp{W})$ such that
  \[
    \forall [\start',\addrend'] \subseteq [\start,\addrend] \ldotp \revokeTemp{W}(r) \nsubsim[n-1] \iota^\pwl_{[\start',\addrend']}
  \]
  Notice $\revokeTemp{W}(r)$ is a $\perma$ region, so $\revokeTemp{W}(r) = W(r)$. Using $r$ as witness, the result is immediate.
\end{proof}

@@

@@

   then  $\npair{((\perm',\gl'),\start,\addrend,\addr)}\in \stdvr(W)$
 \end{lemma}
 \begin{proof}
   TODO
 \end{proof}
